---
title: "GMM_Inference_Explore"
author: "Peng Wang"
date: "6/15/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

## Example 1

```{r simulation for exampel 1}
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')

simu.size=100
no.of.nodes=10
run_simu_example1<-function()
{
# True parameters: 
# True parameters: 
K0 = 3
p0 = c(.30, .25, .45)  
mu0= c(-5, 0, 5)
sigma2.0 = c(1,1,1) 
nn = 250



M.tmp = factor(sample(c(1,2,3), nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

K_h_grid=1:10

K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 200, skip_K_obs = TRUE)
}


simu.size=100
ys.obs=0
set.seed(1045)
for (i in 1:simu.size){
#  set.seed(56+i)
  print(i)
print("sum y")  
sum(ys.obs) %>% print
M.tmp = factor(sample(c(1,2,3), nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
print(nn)
print(sum(rnorm(nn)))
aa<-rnorm(nn)
print("sum aa")
sum(aa) %>% print
us.rel = aa
print("sum u")
sum(us.rel) %>% print
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

print("sum y again")
sum(ys.obs) %>% print

K_h_grid=1:10

K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 2, skip_K_obs = TRUE) ->temp

sum(temp$ys.obs) %>% print
  
}
  



# library(parallel)
cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())


Simu_results_list_example_1<- parReplicate(cl, simu.size, run_simu_example1(), simplify=FALSE)

stopCluster(cl)

K0 = 3
tibble(coverage_confidence = mean(sapply(Simu_results_list_example_1, function(x) K0 %in%x$K_confidence_set )),
       size_confidence = mean(sapply(Simu_results_list_example_1, function(x) length(x$K_confidence_set) )), 
       coverage_candidate = mean(sapply(Simu_results_list_example_1, function(x) K0 %in% c(3, x$K_list_u))),
       length_candidate = mean(sapply(Simu_results_list_example_1, function(x) length(unique(x$K_list_u))+1))
       ) %>% kable
       



```

| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                   1|            2.91|                  1|             2.91|





## Example 1.2, Example 1 with larger sample size of  $n=1000$
```{r simulation for exampel 1.2}
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example1.2"
run_simu_example1.2<-function()
{
# True parameters: 
# True parameters: 
K0 = 3
p0 = c(.30, .25, .45)  
mu0= c(-5, 0, 5)
sigma2.0 = c(1,1,1) 
nn = 1000



M.tmp = factor(sample(c(1,2,3), nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

K_h_grid=1:10

K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 200, skip_K_obs = TRUE)
}


simu.size=100
no.of.nodes=20




# library(parallel)
cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())
Simu_results_list_example_1.2<- parReplicate(cl, simu.size, run_simu_example1.2(), simplify=FALSE)


stopCluster(cl)
K0 = 3


sum_res_simulation(Simu_results_list_example_1.2)->res_table
res_table%>% kable 
       
save.image(paste0(example_names, "_simualation_results.Rdata"))

```

| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                   1|            2.01|                  1|             2.01|


## Example 2, same as example 1 but with closer distance between clusters, looks like a single normal

```{r simulation example 2}
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')

simu.size=100
no.of.nodes=20

run_simu_example2<-function()
{
# True parameters: 
K0 = 3
p0 = c(.30, .25, .45)  
mu0= c(-2.5, 0, 2.5)
sigma2.0 = c(1,1,1) # * 4

## Observed data: 
nn = 250

M.tmp = factor(sample(c(1,2,3), nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

K_h_grid=1:10

K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 200, skip_K_obs = TRUE)
}



# library(parallel)
cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())


Simu_results_list_example2<- parReplicate(cl, simu.size, run_simu_example2(), simplify=FALSE)
K0 = 3
tibble(coverage_confidence = mean(sapply(Simu_results_list_example2, function(x) K0 %in%x$K_confidence_set )),
       size_confidence = mean(sapply(Simu_results_list_example2, function(x) length(x$K_confidence_set) )), 
       coverage_candidate = mean(sapply(Simu_results_list_example2, function(x) K0 %in% c(2, x$K_list_u))),
       length_candidate = mean(sapply(Simu_results_list_example2, function(x) length(unique(x$K_list_u))+1))
       ) %>% kable
       

stopCluster(cl)

```



| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                0.99|            2.84|               0.99|              3.7|

## Example 3 same as example 1 but with different variance

```{r simulation example 3}
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example3"
run_simu_example3<-function(seed_iter)
{
  
set.seed(seed_iter)

K0 = 3
p0 = c(.30, .25, .45)  
mu0= c(-5, 0, 5)
sigma2.0 = c(3,1,4) # * 4
nn = 250

M.tmp = factor(sample(c(1,2,3), nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 200, skip_K_obs = TRUE),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}




simu.size=100
no.of.nodes=20

# library(parallel)
cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())


seed0=1045
set.seed(seed0)
seed_vector<-100*(simu.size)*runif(simu.size)
Simu_results_list_example_3<- parSapply(cl, seed_vector, run_simu_example3, simplify=FALSE)



#Simu_results_list_example_3<- parReplicate(cl, simu.size, run_simu_example3(), simplify=FALSE)
stopCluster(cl)

K0 = 3


sum_res_simulation(Simu_results_list_example_3)->res_table
res_table%>% kable 
       
save.image(paste0(example_names, "_simualation_results.Rdata"))

```


| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                   1|            2.98|                  1|             3.67|



## Example 3 same as example 1 but with different variance

```{r simulation example 3}
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example3"
run_simu_example3<-function(seed_iter)
{
  
set.seed(seed_iter)

K0 = 10
p0 = c(.30, .25, .45)  
mu0= c(-5, 0, 5)
sigma2.0 = c(3,1,4) # * 4
nn = 250

M.tmp = factor(sample(c(1,2,3), nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 200, skip_K_obs = TRUE),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}




simu.size=100
no.of.nodes=20

# library(parallel)
cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())


seed0=1045
set.seed(seed0)
seed_vector<-100*(simu.size)*runif(simu.size)
Simu_results_list_example_3<- parSapply(cl, seed_vector, run_simu_example3, simplify=FALSE)



#Simu_results_list_example_3<- parReplicate(cl, simu.size, run_simu_example3(), simplify=FALSE)

stopCluster(cl)

Simu_results_list_example_3 %>% sapply( function(x) x$K_confidence_set) %>% is.null() %>% sum

K0 = 3


sum_res_simulation(Simu_results_list_example_3)->res_table
res_table%>% kable 
       
save.image(paste0(example_names, "_simualation_results.Rdata"))

```




## Example 4 Chen, Li and Fu JASA 2012 K_0=5, Table 6 Lowest Power Example, N=200

```{r simulation example 4}
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example4"
run_simu_example4<-function(seed_iter)
{
  
set.seed(seed_iter)

K0 = 5
p0 = c(.2, .2, .2, .2, .2)  
mu0= c(-5, -2.5,0,2.5, 5)
sigma2.0 = c(1,1,1,1,1) # * 4
nn = 200

M.tmp = factor(sample(1:K0, nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 200, skip_K_obs = TRUE),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}




simu.size=100
no.of.nodes=20

# library(parallel)
cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())

seed0=2046
set.seed(seed0)
seed_vector<-100*(simu.size)*runif(simu.size)
Simu_results_list_example_4<- parSapply(cl, seed_vector, run_simu_example4, simplify=FALSE)
stopCluster(cl)



Simu_results_list_example_4 %>% sapply( function(x) x$K_confidence_set) %>% is.null() %>% sum
Simu_results_list_example_4 %>% sapply( function(x) x$K_list) 


K0 = 5
sum_res_simulation(Simu_results_list_example_4)->res_table
res_table%>% kable 


       
save.image(paste0(example_names, "_simualation_results.Rdata"))

```



| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                0.03|            2.62|               0.04|             3.41|







## Example 5 Chen, Li and Fu JASA 2012 K_0=5, Table 6 Lowest Power Example, N=400

```{r simulation example 5}
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example5"
run_simu_example5<-function(seed_iter)
{
  
set.seed(seed_iter)

K0 = 5
p0 = c(.2, .2, .2, .2, .2)  
mu0= c(-5, -2.5,0,2.5, 5)
sigma2.0 = c(1,1,1,1,1) # * 4
nn = 400

M.tmp = factor(sample(1:K0, nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 200, skip_K_obs = TRUE),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}




simu.size=100
no.of.nodes=20

# library(parallel)
cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())

seed0=2046
set.seed(seed0)
seed_vector<-100*(simu.size)*runif(simu.size)
Simu_results_list_example_5<- parSapply(cl, seed_vector, run_simu_example5, simplify=FALSE)
stopCluster(cl)



Simu_results_list_example_5 %>% sapply( function(x) x$K_confidence_set) %>% is.null() %>% sum
Simu_results_list_example_5 %>% sapply( function(x) x$K_list) 
Simu_results_list_example_5 %>% sapply( function(x) x$K_hat_obs) %>% table 

K0 = 5
sum_res_simulation(Simu_results_list_example_5)->res_table
res_table%>% kable 


       
save.image(paste0(example_names, "_simualation_results.Rdata"))

```


| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                0.15|            2.83|               0.21|             3.69|







## Example 6 Chen, Li and Fu JASA 2012 K_0=5, Table 6 3rd Row, 

```{r simulation example 6}
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example6"
run_simu_example6<-function(seed_iter)
{
  
set.seed(seed_iter)

K0 = 5
p0 = c(.2, .2, .2, .2, .2)  
mu0= c(-5, -2.5,0,2.5, 5)
sigma2.0 = c(0.6,1.2,0.6,1.2,1) # * 4
nn = 400

M.tmp = factor(sample(1:K0, nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 200, skip_K_obs = TRUE),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}




simu.size=100
no.of.nodes=20

# library(parallel)
cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())

seed0=3047
set.seed(seed0)
seed_vector<-100*(simu.size)*runif(simu.size)
Simu_results_list_example_6<- parSapply(cl, seed_vector, run_simu_example6, simplify=FALSE)
stopCluster(cl)



Simu_results_list_example_6 %>% sapply( function(x) x$K_confidence_set) %>% is.null() %>% sum
Simu_results_list_example_6 %>% sapply( function(x) x$K_list) 

Simu_results_list_example_6 %>% sapply( function(x) x$K_hat_obs) %>% table 
K0 = 5
sum_res_simulation(Simu_results_list_example_6)->res_table
res_table%>% kable 


##Do another run for Repro_size = 400, and repro_size=200


source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example6_2"
run_simu_example6<-function(seed_iter)
{
  
set.seed(seed_iter)

K0 = 5
p0 = c(.2, .2, .2, .2, .2)  
mu0= c(-5, -2.5,0,2.5, 5)
sigma2.0 = c(0.6,1.2,0.6,1.2,1) # * 4
nn = 400

M.tmp = factor(sample(1:K0, nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 400, repro_size = 200, skip_K_obs = TRUE),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}

simu.size=100
no.of.nodes=20



cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())
seed0=4048
set.seed(seed0)
seed_vector<-100*(simu.size)*runif(simu.size)
Simu_results_list_example_6_2<- parSapply(cl, seed_vector, run_simu_example6, simplify=FALSE)
stopCluster(cl)



       
save.image(paste0(example_names, "_simualation_results.Rdata"))




source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example6_3"
run_simu_example6<-function(seed_iter)
{
  
set.seed(seed_iter)

K0 = 5
p0 = c(.2, .2, .2, .2, .2)  
mu0= c(-5, -2.5,0,2.5, 5)
sigma2.0 = c(0.6,1.2,0.6,1.2,1) # * 4
nn = 400

M.tmp = factor(sample(1:K0, nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 1000, repro_size = 200, skip_K_obs = TRUE),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}

simu.size=100
no.of.nodes=20



cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())
seed0=4048
set.seed(seed0)
seed_vector<-100*(simu.size)*runif(simu.size)
Simu_results_list_example_6_3<- parSapply(cl, seed_vector, run_simu_example6, simplify=FALSE)
stopCluster(cl)



       
save.image(paste0(example_names, "_simualation_results.Rdata"))


Simu_results_list_example_6_3 %>% sapply( function(x) x$K_hat_obs) %>% table 
K0 = 5
sum_res_simulation(Simu_results_list_example_6_3)->res_table
res_table%>% kable 



map2(Simu_results_list_example_6, Simu_results_list_example_6_2, function(x,y) c(x$K_confidence_set, y$K_confidence_set) %>%  unique %>% `%in%` (K0,.)) %>% do.call(c, .) %>%  mean



map2(Simu_results_list_example_6, Simu_results_list_example_6_2, function(x,y) c(x$K_confidence_set, y$K_confidence_set) %>%  unique %>% `%in%` (3,.)) %>% do.call(c, .) %>%  mean

```


### First run, repro_M_size=200, repro_size=100

| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                0.51|             3.4|               0.58|             3.81|


### Second run, repro_M_size=400, repro_size=200

| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                0.67|            3.63|               0.74|             4.06|


### Third run, repro_M_size=1000, repro_size=200

| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                0.88|            3.95|               0.91|              4.4|






```{r rerun example 6_3 with fixed variance when obtaining the ccandidates}


source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example6_3R"
run_simu_example6<-function(seed_iter)
{
  
set.seed(seed_iter)

K0 = 5
p0 = c(.2, .2, .2, .2, .2)  
mu0= c(-5, -2.5,0,2.5, 5)
sigma2.0 = c(0.6,1.2,0.6,1.2,1) # * 4
nn = 400

M.tmp = factor(sample(1:K0, nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 1000, repro_size = 200, skip_K_obs = TRUE),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}

simu.size=100
no.of.nodes=20


p_value_vector<-pbsapply(1:100, function(i) (M.mat %*% mu0 + diag(rnorm(nn)) %*% M.mat %*% sigma2.0^.5) %>%as.vector %>%  emtest.norm(m0 = 3) %>% `$`(`P-values`))



cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())
seed0=4048
set.seed(seed0)
seed_vector<-100*(simu.size)*runif(simu.size)
Simu_results_list_example_6_3<- parSapply(cl, seed_vector, run_simu_example6, simplify=FALSE)
stopCluster(cl)



       
save.image(paste0(example_names, "_simualation_results.Rdata"))


```


Table: Table of K+obs
|.  | Freq|
|:--|----:|
|2  |    1|
|3  |   90|
|4  |    8|
|5  |    1|



Table: Coverage of Confidence Sets
| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                   1|            4.43|                  1|             5.56|





```{r rerun example 6_3 with fixed variance and modified version of BIC (+1/n)}
setwd("D:/Dropbox/Repro Sampling General/R Codes")
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example6_3R_mBIC"
run_simu_example6<-function(seed_iter)
{
  
set.seed(seed_iter)

K0 = 5
p0 = c(.2, .2, .2, .2, .2)  
mu0= c(-5, -2.5,0,2.5, 5)
sigma2.0 = c(0.6,1.2,0.6,1.2,1) # * 4
nn = 400

M.tmp = factor(sample(1:K0, nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5


seed_local=2*seed_iter

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 200, repro_size = 200, skip_K_obs = TRUE, seed_local=seed_local),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}

simu.size=100
no.of.nodes=20



cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())
seed0=4048
#set.seed(seed0)
seed_vector<-seed0+ 1:simu.size
Simu_results_list_example_6_3<- parSapply(cl, seed_vector, run_simu_example6, simplify=FALSE)
stopCluster(cl)


save.image(paste0(example_names, Sys.Date(), "_simualation_results.Rdata"))

Simu_results_list_example_6_3 %>% sapply( function(x) x$K_hat_obs) %>% table %>% kable 
K0 = 5
sum_res_simulation(Simu_results_list_example_6_3)->res_table
res_table%>% kable 

```


|.  | Freq|
|:--|----:|
|2  |    1|
|3  |   90|
|4  |    8|
|5  |    1|



| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                   1|            5.03|                  1|             5.39|




```{r rerun example 6_3_chen with fixed variance and modified version of BIC (+1/n)}
setwd("D:/Dropbox/Repro Sampling General/R Codes")
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example6_3R2_Chen"
run_simu_example6<-function(seed_iter)
{
  
set.seed(seed_iter)

K0 = 5
p0 = c(.2, .2, .2, .2, .2)  
mu0= c(-5, -2.5,0,2.5, 5)
sigma2.0 = c(0.6,1.2,0.6,1.2,1)^2 # * 4
nn = 400

M.tmp = factor(sample(1:K0, nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5


seed_local=2*seed_iter

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 200, repro_size = 200, skip_K_obs = TRUE, seed_local=seed_local),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}

simu.size=100
no.of.nodes=20



cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())
seed0=4048
#set.seed(seed0)
seed_vector<-seed0+ 1:simu.size
Simu_results_list_example_6_3<- parSapply(cl, seed_vector, run_simu_example6, simplify=FALSE)
stopCluster(cl)


p_value_vector_chen<-pbsapply(1:100, function(i) (M.mat %*% mu0 + diag(rnorm(nn)) %*% M.mat %*% sigma2.0^.5) %>%as.vector %>%  emtest.norm(m0 = 3) %>% `$`(`P-values`))


save.image(paste0(example_names, Sys.Date(), "_simualation_results.Rdata"))

Simu_results_list_example_6_3 %>% sapply( function(x) x$K_hat_obs) %>% table %>% kable 
K0 = 5
sum_res_simulation(Simu_results_list_example_6_3)->res_table
res_table%>% kable 

```



|.  | Freq|
|:--|----:|
|3  |   67|
|4  |   22|
|5  |   11|


| coverage_confidence| size_confidence| coverage_candidate| length_candidate|
|-------------------:|---------------:|------------------:|----------------:|
|                   1|            6.25|                  1|             7.89|


```{r data analysis SLC data}
setwd("D:/Dropbox/Repro Sampling General/R Codes")
##Data in MixtureInf package
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
data(SLC)
seed_local=7788
set.seed(seed_local)
K_h_grid=1:10
K_infer_SLC<-K_inference_repro_Mu(ys.obs = SLC$SLC, K_h_grid, repro_M_size = 200, repro_size = 200, skip_K_obs = FALSE, seed_local=seed_local)
K_infer_SLC_7788<-K_infer_SLC

saveRDS(K_infer_SLC_7788, "SLC_Data_Seed_7788.RDS")

# 
# source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
# data(SLC)
# seed_local=1122
# set.seed(seed_local)
# K_h_grid=1:10
# K_infer_SLC<-K_inference_repro_Mu(ys.obs = SLC$SLC, K_h_grid, repro_M_size = 200, repro_size = 200, skip_K_obs = FALSE, seed_local=seed_local)
# K_infer_SLC_1122<-K_infer_SLC
# saveRDS(K_infer_SLC_1122, "SLC_Data_Seed_1122.RDS")


SLC_K_2<-GMM(SLC, 2)
SLC_K_3<-GMM(SLC, 3)
SLC_K_4<-GMM(SLC, 4)

mm_density_2<-function(x) sum(SLC_K_2$weights*sapply(1:2, function(i) dnorm(x, SLC_K_2$centroids[i], sd = sqrt(SLC_K_2$covariance_matrices[i]))))

mm_density_3<-function(x) sum(SLC_K_3$weights*sapply(1:3, function(i) dnorm(x, SLC_K_3$centroids[i], sd = sqrt(SLC_K_3$covariance_matrices[i]))))


mm_density_4<-function(x) sum(SLC_K_4$weights*sapply(1:4, function(i) dnorm(x, SLC_K_4$centroids[i], sd = sqrt(SLC_K_4$covariance_matrices[i]))))

hist(SLC$SLC, breaks = 20,probability = T, ylim = c(0,6), xlab = "SLC Measurements", main = "")
lines(seq(0, 0.7,length.out = 1000), sapply(seq(0, 0.7,length.out = 1000), mm_density_2), lty=4, lwd=2 )
lines(seq(0, 0.7,length.out = 1000), sapply(seq(0, 0.7,length.out = 1000), mm_density_3),  lty=2, col="blue", lwd=2 )
lines(seq(0, 0.7,length.out = 1000), sapply(seq(0, 0.7,length.out = 1000), mm_density_4),  lty=1, col="red", lwd=2)
legend(x = 0.5, y = 4, legend = c("K=2", "K=3", "K=4"), col = c("black", "blue", "red"), lty = c(4,2,1))

library(xtable)
tibble(
K=c(2,3,4),
normal_mean=c(
SLC_K_2$centroids %>%  round(digits = 4) %>% paste(collapse = ","),
SLC_K_3$centroids %>%  round(digits = 4) %>% paste(collapse = ","),
SLC_K_4$centroids %>%  round(digits = 4) %>% paste(collapse = ",")
),
normal_sd=c(
SLC_K_2$covariance_matrices %>% sqrt %>%   round(digits = 4) %>% paste(collapse = ","),
SLC_K_3$covariance_matrices %>% sqrt %>%  round(digits = 4) %>% paste(collapse = ","),
SLC_K_4$covariance_matrices %>% sqrt %>%  round(digits = 4) %>% paste(collapse = ",")
),
weights=c(
  SLC_K_2$weights %>%  round(digits = 4) %>% paste(collapse = ","),
SLC_K_3$weights %>%  round(digits = 4) %>% paste(collapse = ","),
SLC_K_4$weights %>%  round(digits = 4) %>% paste(collapse = ",")
)
) %>% xtable() %>% print(include.rownames=FALSE)

```



```{r simulation using settings from SLC data, K0=3}
setwd("D:/Dropbox/Repro Sampling General/R Codes")
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example_SLC_K3"
SLC_K_3<-readRDS("SLC_K_3.RDS")

data(SLC)

K0 = 3
p0 = SLC_K_3$weights  
mu0= SLC_K_3$centroids
sigma2.0 = SLC_K_3$covariance_matrices # * 4
nn = length(SLC$SLC)

M.tmp = factor(sample(1:K0, nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)

run_simu_example_SLC<-function(seed_iter)
{
  
set.seed(seed_iter)
# M.tmp = factor(sample(1:K0, nn, replace = T, prob = p0))
# M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5


seed_local=2*seed_iter

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 200, repro_size = 200, skip_K_obs = TRUE, seed_local=seed_local),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}

simu.size=200
no.of.nodes=20



cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())
seed0=4048
#set.seed(seed0)
seed_vector<-seed0+ 1:simu.size
Simu_results_list_example_SLC<- parSapply(cl, seed_vector, run_simu_example_SLC, simplify=FALSE)
stopCluster(cl)

# 
p_value_vector_chen<-pbsapply(1:simu.size, function(i) Simu_results_list_example_SLC[[i]]$ys.obs %>%as.vector %>%  emtest.norm(m0 = 2) %>% `$`(`P-values`))

(p_value_vector_chen<0.05) %>% sum


save.image(paste0(example_names, Sys.Date(), "_simualation_results.Rdata"))

Simu_results_list_example_SLC %>% sapply( function(x) x$K_hat_obs) %>% table %>% kable 
sum_res_simulation(Simu_results_list_example_SLC)->res_table
add_column(res_table, Chen_power=(p_value_vector_chen<0.05) %>%mean) %>% kable
res_table%>% kable 
```


|.  | Freq|
|:--|----:|
|1  |   12|
|2  |  175|
|3  |   13|

| coverage_confidence| SE_coverage_confidence| size_confidence| SE_size_confidence| coverage_candidate| SE_coverage_candidate| length_candidate| SE_length_candidate| Chen_power|
|-------------------:|----------------------:|---------------:|------------------:|------------------:|---------------------:|----------------:|-------------------:|----------:|
|                0.99|              0.0070533|           2.975|          0.0488241|                  1|                     0|            3.515|           0.0548994|       0.26|

Majority of the confidence set is {2,3,4}




```{r simulation using settings from SLC data, K0=4}
setwd("D:/Dropbox/Repro Sampling General/R Codes")
source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
example_names<-"example_SLC_K4"
SLC_K_4<-readRDS("SLC_K_4.RDS")

data(SLC)

K0 = 4
p0 = SLC_K_4$weights  
mu0= SLC_K_4$centroids
sigma2.0 = SLC_K_4$covariance_matrices # * 4
nn = length(SLC$SLC)

run_simu_example_SLC<-function(seed_iter)
{
  
set.seed(seed_iter)
M.tmp = factor(sample(1:K0, nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
us.rel = rnorm(nn)
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5


seed_local=2*seed_iter

K_h_grid=1:10

tryCatch(K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 400, repro_size = 200, skip_K_obs = TRUE, seed_local=seed_local),
         error = function(c) return(list(K_confidence_set_1=NULL,
              Nuclear_values_1=NULL,
              K_confidence_set_2=NULL,
              Nuclear_values_2=NULL,
              ys.obs=ys.obs
  )))
}

simu.size=200
no.of.nodes=20



cl <- makePSOCKcluster(no.of.nodes)
clusterEvalQ(cl,library(tidyverse))
clusterEvalQ(cl,library(flexmix))
clusterEvalQ(cl,library(ClusterR))
clusterEvalQ(cl,library(pbapply))
clusterExport(cl,ls())
seed0=4048
#set.seed(seed0)
seed_vector<-seed0+ 1:simu.size
Simu_results_list_example_SLC<- parSapply(cl, seed_vector, run_simu_example_SLC, simplify=FALSE)
stopCluster(cl)

# 
p_value_vector_chen<-pbsapply(1:simu.size, function(i) Simu_results_list_example_SLC[[i]]$ys.obs %>%as.vector %>%  emtest.norm(m0 = 2) %>% `$`(`P-values`))



# 
p_value_vector_chen_m03<-pbsapply(1:simu.size, function(i) Simu_results_list_example_SLC[[i]]$ys.obs %>%as.vector %>%  emtest.norm(m0 = 3) %>% `$`(`P-values`))



save.image(paste0(example_names, Sys.Date(), "_simualation_results.Rdata"))

Simu_results_list_example_SLC %>% sapply( function(x) x$K_hat_obs) %>% table %>% kable 
sum_res_simulation(Simu_results_list_example_SLC)->res_table
add_column(res_table, Chen_power=(p_value_vector_chen<0.05) %>% mean) %>% add_column( Chen_power_K03=(p_value_vector_chen_m03<0.05) %>% mean) %>% kable
res_table%>% kable 



Simu_results_list_example_SLC %>% sapply(function(x) x$K_confidence_set %>% sort %>% paste0(collapse = " ")) %>% table
```


Table:Simulation Results
| coverage_confidence| size_confidence| coverage_candidate| length_candidate| Chen_power| Chen_power_K03|
|-------------------:|---------------:|------------------:|----------------:|----------:|--------------:|
|               0.965|           3.655|              0.965|             4.16|      0.485|           0.07|


Table: Frequency of Estimation
|.  | Freq|
|:--|----:|
|1  |    4|
|2  |  186|
|3  |   10|



```{r some weird behaviour of R}

Simu_results_list_example_3<-list()
ys.obs=0

for (i in 1:simu.size){
#  set.seed(56+i)
  set.seed(seed_vector[i])
print("sum y")  
sum(ys.obs) %>% print
M.tmp = factor(sample(c(1,2,3), nn, replace = T, prob = p0))
M.mat = model.matrix(~ M.tmp - 1)
print(nn)
aa<-rnorm(nn)
print("sum aa")
sum(aa) %>% print
us.rel = aa
print("sum u")
sum(us.rel) %>% print
ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5

print("sum y again")
sum(ys.obs) %>% print

K_h_grid=1:10
K_inference_repro_Mu(ys.obs,K_h_grid, repro_M_size = 10, skip_K_obs = TRUE) ->Simu_results_list_example_3[[i]]
print("sum y after run")

sum(Simu_results_list_example_3[[i]]$ys.obs) %>% print
  
}
  



```




```{r more weird behavrior of R}
> ##Data in MixtureInf package
> source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
> data(SLC)
> set.seed(7788)
> K_h_grid=1:10
> K_infer_SLC<-K_inference_repro_Mu(ys.obs = SLC$SLC, K_h_grid, repro_M_size = 200, repro_size = 200, skip_K_obs = FALSE)
  |                                                  | 0 % ~calculating  [1] -6.599025
1 : * * *
2 : * * *
3 : * * *
4 : * * *
5 : * * *
6 : * * *
7 : * * *
8 : * * *
9 : * * *
10 : * * *
[1] -4.27981
1 : * * *
2 : * * *
3 : * * *
4 : * * *
5 : * * *
6 : * *


> source('D:/Dropbox/Repro Sampling General/R Codes/Functions_and_Packages.R')
> data(SLC)
> set.seed(1122)
> K_h_grid=1:10
> K_infer_SLC<-K_inference_repro_Mu(ys.obs = SLC$SLC, K_h_grid, repro_M_size = 200, repro_size = 200, skip_K_obs = FALSE)
  |                                                  | 0 % ~calculating  [1] -6.599025
1 : * * *
2 : * * *
3 : * * *
4 : * * *
5 : * * *
6 : *

```



```{r}
# clusterExport(cl,c("ys.obs", "K_h_grid"))
# Mu_matrix_2<-parReplicate(cl, 100, stepFlexmix(ys.obs ~ rnorm(length(ys.obs)), k = K_h_grid) %>% getModel("BIC") %>% '@'(cluster))


# 
# no_of_nodes = 10
# 
# #library(progressr)
# cl <- makeCluster(no_of_nodes)
# registerDoParallel(cl)
# 
# #p <- progressor(along = 1:simu.size)
# K_inference_simulation<-foreach(i=1:simu.size, .packages = c("Matrix", "ClusterR", "tidyverse","pbapply"),.export = ls(globalenv()), .verbose = FALSE ) %dopar% 
#            {
#             M.tmp = factor(sample(c(1,2,3), nn, replace = T, prob = p0))
#             M.mat = model.matrix(~ M.tmp - 1)
#             us.rel = rnorm(nn)
#             ys.obs = M.mat %*% mu0 + diag(us.rel) %*% M.mat %*% sigma2.0^.5
#            # p(sprintf("i=%g", i/simu.size))
# 
#             All<-K_inference_repro(ys.obs, K_h_grid=1:10)
# 
#            } 
# stopCluster(cl)
# 
# K_coverage <-sapply(K_inference_simulation, function(x) K0 %in% x$K_confidence_set) %>% mean
# Width <-  sapply(K_inference_simulation, function(x)  length(x$K_confidence_set)) %>% mean
```

